### 2025-01-11 manuscript/manuscript.tex
typo in bib and add author

\begin{center}
    {\Huge Island-Wide Soil integration: the case of Crete}\\[2em]
    {\large Savvas Paragkamian, Evangelos Pafilis, Georgios Kotoulas}\\[1em]
    {\large \today}
\end{center}

>>>>

\begin{center}
    {\Huge Island-Wide Soil integration: the case of Crete}\\[2em]
    {\large Savvas Paragkamian, Panagiotis F. Sarris, Evangelos Pafilis, Georgios Kotoulas}\\[1em]
    {\large \today}
\end{center}
